### 2022-06-13 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}[H]
	\centering
		\includegraphics[width=0.7\linewidth]{figures/poumm_parameter_estimates.png}
		\caption{Posterior distributions compared to the prior for POUMM parameter estimates based on SHCS data. We ran two different MCMC chains to ensure the estimates converged. The black point on the x-axis shows the posterior mean value, which was used to estimate the pathogen- and non-pathogen effects on spVL.}
\label{fig:poumm-parameters}
\end{figure}

@@

@@

>>>>

\begin{figure}[H]
	\centering
		\includegraphics[width=0.7\linewidth]{figures/poumm_parameter_estimates.png}
		\caption{Posterior distributions compared to the prior for POUMM parameter estimates based on SHCS data. We ran two different MCMC chains to ensure the estimates converged.}
\label{fig:poumm-parameters}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = \linewidth]{figures/qdr_on_tree_arboricola.png}
	\caption{Inferred \emph{X. arboricola} phylogeny with tips colored by (A) calculated QDR, (B) estimated non-pathogen effects on QDR and (C) estimated pathogen effects on QDR.}
	\label{fig:qdr-on-tree}
	\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.462\linewidth]{figures/trait_values_arboricola.png}
	\caption{A comparison of measured (calculated) QDR values versus our estimated non-pathogen effect on QDR for each selected \emph{A. thaliana} host - \emph{X. arboricola} pathogen pairing selected for the GWAS. The histograms show the marginal distribution of each value across the individual pairings.}
	\label{fig:trait-comparison-qdr}
	\end{center}
\end{figure}

\begin{figure}[H]
	\centering
		\includegraphics[width=0.7\linewidth]{figures/poumm_parameter_estimates_arboricola.png}
		\caption{Posterior distributions compared to the prior for POUMM parameter estimates based on \emph{A. thaliana}-\emph{X. arboricola} data. We ran two different MCMC chains to ensure the estimates converged.}
\label{fig:poumm-parameters-qdr}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{figures/gwas_results_xanthomonas.png}
	\caption{Results from comparative GWAS on \emph{A. thaliana}-\emph{X. arboricola} QDR. Points are association p-values for the same \emph{A. thaliana} host variants in GWAS with two different response variables. On the left, we used unmodified (total) QDR values. On the right, we used our estimates for the non-pathogen effects on QDR. The alternating shades correspond to different chromosomes. The dashed lines show significance at $\alpha$ = 0.05 with a Bonferroni correction for multiple-testing.}
	\label{fig:gwas-results-qdr}
\end{figure}

@@

\begin{table}[H]
\caption{POUMM parameter estimates for QDR based on \emph{A. thaliana}-\emph{X. arboricola} data data. HPD = Highest posterior density.}
	\begin{tabularx}{\linewidth}{XXX} \hline 
	Parameter & Posterior mean & 95\% HPD \\ \hline 
	${g_{0}}$ & 0.40 & (0.01, 0.78) \\
	$\theta$ & 0.39 & (0.30, 0.49) \\
	$\sigma$ & 0.03 & (0.0, 0.06) \\
	$\alpha$ & 0.03 & (0.0, 0.05) \\
	$\sigma_e$ & 0.18 & (0.08, 0.27) \\ 
	$H^2_{\bar{t}}$ & 0.33 & (0.0, 0.77) \\ \hline
	\end{tabularx}
	\label{tab:POUMM-parameters-our-estimates-qdr}
\end{table}
